---
title: "R Notebook"
output: html_notebook
---

## Histogram Of Share prices

```{r}
hist(Tut1_shareprices$shareprice, main = "Histogram Of Share Prices", xlab = "Share Prices", col = "blue", border = "white")
```

## Test for Normality

```{r}
shapiro_test_result = shapiro.test(Tut1_shareprices$shareprice)
shapiro_test_result
```

We can conclude the data in normally Distributed

## Linear Model with No Categorical Variables and Unscaled

```{r}
model1 = lm(Tut1_shareprices$shareprice ~ Tut1_shareprices$turnover+Tut1_shareprices$leverage)
summary(model1)
```

The model explains 43% of the variance in share price using turnover and leverage. The Model is significant. Residuals look to be normally distributed we can see leverage is not a significant variable in the model bu rather turnover

## Handling Categorical variables

#### convert categorical variable to a factor

```{r}
Tut1_shareprices$sector = factor(Tut1_shareprices$sector)
```

#### Creating Dummy Variables

Create dummy variables for the categorical columns 'sector' and 'companysize'

```{r}
dummies_sector = model.matrix(~ sector, data=Tut1_shareprices)
dummies_sector = dummies_sector[,-1]
dummies_sector
dummies_size = model.matrix(~ companysize, data=Tut1_shareprices)
dummies_size = dummies_size[,-1]
dummies_size
```

#### adding dummy variables to dataframe

```{r}
df_with_dummies = Tut1_shareprices 
df_with_dummies = cbind(Tut1_shareprices,dummies_sector)
df_with_dummies = cbind(df_with_dummies, dummies_size)
df_with_dummies
```

## Linear Models with Categorical variables

```{r}
model2 = lm(shareprice ~ turnover+leverage+sectorInsurance+sectorLeisure+companysizeMedium+companysizeSmall, data = df_with_dummies)
summary(model2)
```

we can see the model explains 82% of the variation in Shareprice. the model is significant in reducing unexplained variation. leverage is the only non significant variable. The smaller the company the higher the shareprice or a medium size results in an increase in shareprice of 116 and 131 for small companies. 
## StepWise Backwards Regression
```{r}
step(model2,direction = 'backward', test="F")
```
## StepWise Forwards Regression
```{r}
step(model2, test="F")
```
## Scaled Linear Model
```{r}
model3 = lm(scale(shareprice) ~ scale(turnover)+scale(leverage)+scale(sectorInsurance)+scale(sectorLeisure)+scale(companysizeMedium)+scale(companysizeSmall), data = df_with_dummies)
summary(model3)
```


